---
title: "Project_1"
author: "Charles, Lei, John"
date: "2/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(leaps)
library(caret)
library(car)


#Set path to housing data.
# JR - Changed path to be relative path assuming rproj file in same directory as rmd files. 
#       Should help with running it on separate workstations
Project <- "/Users/Chase/Desktop/MSDS/MSDS6306/Homework/SMU_MSDS_Homework/Case_Study_1/DS6372-GroupProject1/ImportedFiles/train_clean_final.csv"

HousingData <- read.csv(Project)
dim(HousingData)

```
```{r}
####UPDATE 1 EDA ####
#Too many missing values, remove: in LotFrontage 259, FirePlaceQu 690, PoolQC 1453,MiscFeature 1406
# Fence 1179, actually not missing value but one level of factor, need transform. or how to deal with it??suggestion? remove for now for further analysis.
#These have less than  100 missing values, keep in dataset: Alley, BsmtQual, BsmtCond, BsmtExposure, BsmtFinType1, BsmtFinType2, GarageType, GarageYrBlt, GarageFinish, GarageQual, GarageCond, MasVnrArea 8


#Report NA count, put in data frame for easier display options using kable
naCountDF <-as.data.frame(sapply(HousingData, function(x) sum(length(which(is.na(x))))))
names(naCountDF) <- ("NA Count") # rename columns

# Print the NA Counts by State

library(kableExtra)
kable(naCountDF,format="html", caption="Table -NA Count (NA=blanks)",align='c') %>% 
  kable_styling(bootstrap_options = "striped", full_width = F)

```

####EDA, find out the column index for "FireplaceQu"
```{r}
#str(HousingData)

which( colnames(HousingData)=="FireplaceQu" )

```
####Removes unnessary predictor columns from dataset
```{r}

Housing <- HousingData[, -c(1,4,7,15,58,73:76,79)] #Removes unnessary predictor columns from dataset
#Features removed: Id, Alley, Condition2, PoolQC, Fense, MiscFeature, MiscVal, SaleType

#4 LotFrontage too mnay missing data  259
#FireplaceQu has need to be removed

#dim(Housing)
#(1460   71)

head(Housing)
```
####EDA
```{r}
#str(Housing)
```

```{r Train and Test Samples}
#Following code creates training and test samples. 
set.seed(1234)
index<-sample(1:dim(Housing)[1],1460/2,replace=F)
train<-Housing[index,]
test<-Housing[-index,]

#Forward
reg.fwd<-regsubsets(SalePrice~.,data=train, method = "forward", really.big = T, nvmax = 20)

coef(reg.fwd,3)

summary(reg.fwd)$adjr2
summary(reg.fwd)$rss
summary(reg.fwd)$bic


par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:21,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

adjr2<-summary(reg.fwd)$adjr2
plot(1:21,adjr2,type="l",ylab="Adjusted R-squared",xlab="# of predictors")
index<-which(adjr2==max(adjr2))
points(index,adjr2[index],col="red",pch=10)

rss<-summary(reg.fwd)$rss
plot(1:21,rss,type="l",ylab="train RSS",xlab="# of predictors")
index<-which(rss==min(rss))
points(index,rss[index],col="red",pch=10)


car::vif(lm(SalePrice~HouseStyle+GrLivArea+SaleCondition,data=Housing))

housing.fwdfit<-lm(SalePrice~HouseStyle+GrLivArea+SaleCondition, data = train)

par(mfrow=c(2,2))
plot(housing.fwdfit)
```

```{r Backward}
#Backward
reg.back<-regsubsets(SalePrice~.,data=train, method = "backward", really.big = T, nvmax = 20)

coef(reg.back,3)

summary(reg.back)$adjr2
summary(reg.back)$rss
summary(reg.back)$bic


par(mfrow=c(1,3))
bics<-summary(reg.back)$bic
plot(1:21,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

adjr2<-summary(reg.back)$adjr2
plot(1:21,adjr2,type="l",ylab="Adjusted R-squared",xlab="# of predictors")
index<-which(adjr2==max(adjr2))
points(index,adjr2[index],col="red",pch=10)

rss<-summary(reg.back)$rss
plot(1:21,rss,type="l",ylab="train RSS",xlab="# of predictors")
index<-which(rss==min(rss))
points(index,rss[index],col="red",pch=10)


car::vif(lm(SalePrice~OverallQual+Functional+Fireplaces,data=Housing))

housing.backfit<-lm(SalePrice~OverallQual+Functional+Fireplaces, data = train)

par(mfrow=c(2,2))
plot(housing.backfit)
```

```{r Stepwise}
#Stepwise
reg.step<-regsubsets(SalePrice~.,data=train, method = "seqrep", really.big = T, nvmax = 20)

coef(reg.step,3)

summary(reg.step)$adjr2
summary(reg.step)$rss
summary(reg.step)$bic


par(mfrow=c(1,3))
bics<-summary(reg.step)$bic
plot(1:21,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

adjr2<-summary(reg.step)$adjr2
plot(1:21,adjr2,type="l",ylab="Adjusted R-squared",xlab="# of predictors")
index<-which(adjr2==max(adjr2))
points(index,adjr2[index],col="red",pch=10)

rss<-summary(reg.step)$rss
plot(1:21,rss,type="l",ylab="train RSS",xlab="# of predictors")
index<-which(rss==min(rss))
points(index,rss[index],col="red",pch=10)


car::vif(lm(SalePrice~OverallQual+GarageType+SaleCondition,data=Housing))

housing.stepfit<-lm(SalePrice~OverallQual+GarageType+SaleCondition, data = train)

par(mfrow=c(2,2))
plot(housing.stepfit)
```


```{r}
summary(housing.fwdfit)
summary(housing.backfit)
summary(housing.stepfit)

```


###Lasso
```{r}
library(glmnet)

# JR - Added line to eliminate NAs.  Not sure if correct solution, but allowed lasso to run.
# https://stackoverflow.com/questions/6447708/model-matrix-generates-fewer-rows-than-original-data-frame
train <- na.omit(train)

test <- na.omit(test)

#Formatting data for GLM net
x=model.matrix(SalePrice~.,train)[,-1]
y=log(train$SalePrice)


xtest<-model.matrix(SalePrice~.,test)[,-1]
ytest<-log(test$SalePrice)

#dim(train)
#str(train)
#str(x)
#str(y)

grid=10^seq(10,-2, length =730)
lasso.mod=glmnet(x,y,alpha=1, lambda =grid)

cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
plot(cv.out)


bestlambda<-cv.out$lambda.min  #Optimal penalty parameter.  You can make this call visually.
lasso.pred=predict (lasso.mod ,s=bestlambda ,newx=xtest)

testMSE_LASSO<-mean((ytest-lasso.pred)^2)
testMSE_LASSO


coef(lasso.mod,s=bestlambda)
```


####Update 2 two way anova####
#Q: check independent assumption of predictors?
```{r}
#create a data frame with OUTPUT SalePrice AND two catagorical predictors Neighborhood 25 levels, HouseStyle 8 levels for two way anova

#dim(Housing)
#str(Housing)
#which( colnames(HousingData)=="Neighborhood" )

#which( colnames(HousingData)=="HouseStyle" )
#which( colnames(HousingData)=="SalePrice" )

HousingANOVA <- Housing[, c(10,13,71)]

str(HousingANOVA )
head(HousingANOVA )

```

#Provide a means plot of the data.
```{r}
#Provide a means plot of the data.
attach(HousingANOVA)
mysummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)),min(x), max(x), IQR(x))
  names(result)<-c("N","Mean","SD","SE","MIN","MAX", "IQR")
  return(result)
}
sumstats<-aggregate(SalePrice~Neighborhood*HouseStyle,data=HousingANOVA,mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])
sumstats

ggplot(sumstats,aes(x=Neighborhood,y=Mean,group=HouseStyle,colour=HouseStyle))+
  ylab("SalePrice")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SE,ymax=Mean+SE),width=.1)
  
#SD as error bar
  ggplot(sumstats,aes(x=Neighborhood,y=Mean,group=HouseStyle,colour=HouseStyle))+
  ylab("SalePrice")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
  
  

```
#### Fit a nonadditive 2 way anova model to the data set and provide the residual diagnostics. 
```{r}

  #Fit a nonadditive 2 way anova model to the data set and provide the residual diagnostics.
  model.fit<-aov(SalePrice~Neighborhood+HouseStyle+Neighborhood*HouseStyle,data=HousingANOVA)
par(mfrow=c(1,2))
plot(model.fit$fitted.values,model.fit$residuals,ylab="Resdiduals",xlab="Fitted")
qqnorm(model.fit$residuals)

#residuals look fan out--non-constant variance, QQplot does not look normal, so decide to log transform SalePrice
```

####log transform SalePrice
```{r}
HousingANOVA$LogSalePrice=log(HousingANOVA$SalePrice)
str(HousingANOVA )
head(HousingANOVA )

```

###mean plot of transformed data
```{r}
#Provide a means plot of the data.
attach(HousingANOVA)
mysummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)),min(x), max(x), IQR(x))
  names(result)<-c("N","Mean","SD","SE","MIN","MAX", "IQR")
  return(result)
}
sumstats<-aggregate(LogSalePrice~Neighborhood*HouseStyle,data=HousingANOVA,mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])
sumstats

ggplot(sumstats,aes(x=Neighborhood,y=Mean,group=HouseStyle,colour=HouseStyle))+
  ylab("SalePrice")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SE,ymax=Mean+SE),width=.1)
  
#SD as error bar
  ggplot(sumstats,aes(x=Neighborhood,y=Mean,group=HouseStyle,colour=HouseStyle))+
  ylab("SalePrice")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
```
#fit
#Q: how to check for outlier?
```{r}
 #Fit a nonadditive 2 way anova model to transformed data and provide the residual diagnostics.
  model.fit<-aov(LogSalePrice~Neighborhood+HouseStyle+Neighborhood*HouseStyle,data=HousingANOVA)
par(mfrow=c(1,2))
plot(model.fit$fitted.values,model.fit$residuals,ylab="Resdiduals",xlab="Fitted")
qqnorm(model.fit$residuals)

# the normality assumption met after log transformation of y

```

####First layer of test. High level test. Provide the type 3 ANOVA F-tests. Type III SS tested on interactions (the presence of a main effect after the other main effect and interaction)
```{r}
#provide the type 3 ANOVA F-tests
library(car)
Anova(model.fit,type=3)
```
####Mutiple testing corrections

```{r}
TukeyHSD(model.fit,"Background",conf.level=.95)
```
####Second layer of test. write contrast. 
```{r}

```
